EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-12 draft.tex
OK, revised, this is done

% Maybe these three sections should be merged; they are all experimental set up and the two next ones start with "experimental"
% (and he next one too) - JJ
% done - Mario 
\section{Container-based application} 
\label{docker}

@@

In the case of the first level of integration, developers
can implement a new stateless Docker container following
the description in the previous section (\ref{workers}). The worker
container executes a daemon that continuously pulls messages from the input queue
on the Redis host specified as an environment variable {\texttt REDIS\_HOST}. If the new
population-based algorithm is written in Python, developers can base the new
implementation on the provided worker container image, adding a new algorithm
function and worker and modifying the \texttt{main.py} file. 
The worker must include a constructor with the configuration dictionary 
(see Listing \ref{code:config}) as the only parameter, and call a the new function 
with the required parameters, unpacking them from the configuration dictionary if necessary.
All the code of the EvoSwarm Application is published with the open source MIT license.
% say which function, what's its API, how can you test it - JJ
% this is not an API the need to write their own - Mario
% We can write an API later - M
% Anyway you need to say what is the signature of the function. 
% Also, if they can use the existing implementation, you need to specify the license - JJ u
% Any reaction to this? - JJ
% I forgot to put done, but I added in the above paragraphs. It was correct? - Mario

@@

container %maybe you should specify more, at the beginning of the section, 
% what is the current setup, what containers are there, what libraries are being used, and so on. - JJ
% The previous section talks about, can you have look? Maybe I should move it to this one. - Mario
% If not, I will add a remainder, something like: following from the setup described in the previous section... - M  
to specify additional configuration options. For instance,  % related to? What do you mean here? - done Mario 
in the current configuration message (see Listing \ref{code:config})
workers executing a GA, initialize the mutation and crossover 
probabilities randomly from a specific range of values. Users specify
this range on the experiment configuration. 
Migration between populations is independent of the type of algorithm, as the
controller treats messages as the same type of objects. But developers could
also change the controller to specify new rules of operation, for instance, to
change the type of migration depending on the algorithm. 
For example, in the case of swarm-based algorithms,  migration between  
populations (swarms) can follow a topology, indicating valid connections 
between them (i.e., ring or hypercube). The controller
can apply these rules selectively only to swarm-based algorithms. 
In general, these configuration options will be algorithm and library specific.

On either level of integration and after making the changes outlined before,
algorithm developers can upload the container 
definition or images directly to a public repository like DockerHub. 
% Clarify what you need to change in those images. 
% Added a brief comment at the beginning  - M
% Will you need to 
% just rebuild the image with new code, or something else? - JJ
% That and document your work, talk about this at the end - M
% We need to document our own images :) - M

@@

% Besides addressing the concerns of a reviewer, you should mention how this is 
% related to the overall objective of the paper, saying this contributes to
% reproducibility or to be able to do it on the cloud  - Jj
% Added the lines bellow - Mario

>>>>

% Maybe these three sections should be merged; they are all experimental set up and the two next ones start with "experimental"
% (and he next one too) - JJ
% done - Mario
% But also change title? - JJ
\section{Container-based application} 
\label{docker}

@@

In the case of the first level of integration, developers
can implement a new stateless Docker container following
the description in the previous section (\ref{workers}). The worker
container executes a daemon that continuously pulls messages from the input queue
on the Redis host specified as an environment variable {\texttt REDIS\_HOST}. If the new
population-based algorithm is written in Python, developers can base the new
implementation on the provided worker container image, adding a new algorithm
function and worker and modifying the \texttt{main.py} file. 
The worker must include a constructor with the configuration dictionary 
(see Listing \ref{code:config}) as the only parameter, and call a the new function 
with the required parameters, unpacking them from the configuration dictionary if necessary.
All the code of the EvoSwarm Application is published with the open source MIT license.

@@

container
in the current configuration message (see Listing \ref{code:config})
workers executing a GA, initialize the mutation and crossover 
probabilities randomly from a specific range of values. Users specify
this range on the experiment configuration. 
Migration between populations is independent of the type of algorithm, as the
controller treats messages as the same type of objects. But developers could
also change the controller to specify new rules of operation, for instance, to
change the type of migration depending on the algorithm. 
For example, in the case of swarm-based algorithms,  migration between  
populations (swarms) can follow a topology, indicating valid connections 
between them (i.e., ring or hypercube). The controller
can apply these rules selectively only to swarm-based algorithms. 
In general, these configuration options will be algorithm and library specific.

On either level of integration and after making the changes outlined before,
algorithm developers can upload the container 
definition or images directly to a public repository like DockerHub.

@@
